Ethnicity sensitive author disambiguation of semi-labeled corpora of scientific articles

### 2015-08-25 paper/paper.tex
notations

Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
p_{N-1}\}$ along with the set of unique individuals ${\cal A} = \{ a_0, ...,
a_{M-1}\}$ having together authored all publications in ${\cal P}$.  Let us
define a signature $s \in p$ from a publication as a unique piece of
information identifying one of the authors of $p$ (e.g., the author name, his
affiliation, along with any other metadata that can be derived from $p$, as illustrated in Figure~\ref{fig:signature}). Let us
denote by ${\cal S} = \{ s | s \in p, p \in {\cal P} \}$ the set of all
signatures that can be extracted from all publications in ${\cal P}$ and
by $S=|{\cal S}|$ the total number of signatures.

@@

As in previous works, the first part of our algorithm consists in dividing
signatures ${\cal S}$ into disjoint subsets ${\cal S}_{b_0}, ..., {\cal
S}_{b_{K-1}}$, or \textit{blocks} \citep{fellegi69}, and then to carry out
author disambiguation independently on each one of these blocks. In doing so,
computational complexity of clustering (see Section~\ref{methods:clustering})
typically reduces from $O(S^2)$ to $O(\sum_b S_b^2)$, which becomes much more
tractable as the number of signatures increases. Since disambiguation is
performed independently per block, a good blocking strategy should ideally be
designed such that signatures from the same author are all mapped to the same
block, otherwise directly preventing their correct clustering in later stages. As a
result, blocking should balance between reduced complexity and maximum recall.

>>>>

Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
p_{N-1}\}$ along with the set of unique individuals ${\cal A} = \{ a_0, ...,
a_{M-1}\}$ having together authored all publications in ${\cal P}$.  Let us
define a signature $s \in p$ from a publication as a unique piece of
information identifying one of the authors of $p$ (e.g., the author name, his
affiliation, along with any other metadata that can be derived from $p$, as illustrated in Figure~\ref{fig:signature}). Let us
denote by ${\cal S} = \{ s | s \in p, p \in {\cal P} \}$ the set of all
signatures that can be extracted from all publications in ${\cal P}$.

@@

As in previous works, the first part of our algorithm consists in dividing
signatures ${\cal S}$ into disjoint subsets ${\cal S}_{b_0}, ..., {\cal
S}_{b_{K-1}}$, or \textit{blocks} \citep{fellegi69}, and then to carry out
author disambiguation independently on each one of these blocks. In doing so,
computational complexity of clustering (see Section~\ref{methods:clustering})
typically reduces from $O(|{\cal S}|^2)$ to $O(\sum_b |{\cal S}_b|^2)$, which becomes much more
tractable as the number of signatures increases. Since disambiguation is
performed independently per block, a good blocking strategy should ideally be
designed such that signatures from the same author are all mapped to the same
block, otherwise directly preventing their correct clustering in later stages. As a
result, blocking should balance between reduced complexity and maximum recall.
